Results

### 2021-07-27 Analysis/03_Summarise_results.Rmd
Update 03_Summarise_results.Rmd
Added fancy plot!

```{r}
## Loading the functions
source("../Functions/extract.table.R")
source("../Functions/plot.metric.results.R")
source("../Functions/paired.tests.R")
source("../Functions/split.metric.R")
source("../Functions/fit.model.rm.R")
source("../Functions/fancy.table.R")
```

@@

  * [x]1. reworking the scaling
  * [ ]2. plotting the metrics per stressors (i.e. all metrics for each stressor).
    `TODO: re-work the plots (15 rows * 4 columns; each row is a metric and contains the lines for the 4 rarefactions; each column is a stressor)`
  * [x]3. fitting a linear model per metric per stressor to rank models based on their r2
  * [x]4. t-test (paired) of difference between each random score and the stressor
    `TODO 3+4: results table per metric`
  * [ ]5. run a psych-style pairwise comparison between each scaled metric
  * [ ]6. put the results in the context of the expectation table from the paper (Null vs process.docx)

@@

```{r}
## Extracting all the scaled results
scaled_results <- extract.table(all_results, scale.method = "between")
```

@@

>>>>

```{r}
## Loading the functions
source("../Functions/extract.table.R")
source("../Functions/plot.metric.results.R")
source("../Functions/paired.tests.R")
source("../Functions/split.metric.R")
source("../Functions/fit.model.rm.R")
source("../Functions/fancy.table.R")
source("../Functions/fancy.plot.R")
```

@@

  * [x]1. reworking the scaling
  * [x]2. plotting the metrics per stressors (i.e. all metrics for each stressor).
    `TODO: re-work the plots (15 rows * 4 columns; each row is a metric and contains the lines for the 4 rarefactions; each column is a stressor)`
  * [x]3. fitting a linear model per metric per stressor to rank models based on their r2
  * [x]4. t-test (paired) of difference between each random score and the stressor
  * [ ]5. run a psych-style pairwise comparison between each scaled metric
  * [ ]6. put the results in the context of the expectation table from the paper (Null vs process.docx)

@@

```{r}
## Extracting all the scaled results
scaled_results <- extract.table(all_results, scale.method = "between")
scaled_within <- extract.table(all_results, scale.method = "within")
```

@@

# Plots per stressor

```{r, fig.width = 8, fig.height = 12}
fancy.plot(scaled_results, col = c("blue", "orange"))
```

Here is the visualisation of the results per stressor and per metric.

# Plots per metric
